---
title: "Class11-section6"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:
```{r}
library(bio3d)
install.packages(c("devtools", "RCurl", "XML"))
library(devtools)
install_bitbucket("Grantlab/bio3d", subdir="ver_devel/bio3d/")

aa <- get.seq("1ake_A")
b <-hmmer(aa)

# Plot a summary of search results  
hits <- plot(b)

head(hits$pdb.id)
```

```{r}
# Fetch PDBs 
files <- get.pdb(hits$pdb.id, path = "pdbs", split = TRUE, gzip = TRUE) 

# Align structures 
pdbs <- pdbaln(files)

# Vector containing PDB codes 
ids <- basename.pdb(pdbs$id)

# Draw schematic alignment   
plot(pdbs, labels=ids)
```


## Including Plots

You can also embed plots, for example:



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
