---
title: "Class11_git"
output: github_document
---

```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```
install.packages("bio3d")
library(bio3d)
file.name <- get.pdb("1hsg")

hiv <- read.pdb(file.name)
prot <- trim.pdb(hiv, "protein")  
lig <- trim.pdb(hiv, "ligand")
 
write.pdb(prot, file="1hsg_protein.pdb")  
write.pdb(lig, "1hsg_ligand.pdb")
```
```
library(bio3d) 
res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
```
```{r}
res <- read.pdb("all.pdbqt", multi=TRUE)
ori <- read.pdb("1hsg_ligand.pdbqt")
rmsd(ori, res)
```

## Including Plots

You can also embed plots, for example:

```
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:


```{r}
library(bio3d)
# Download some example PDB files
ids <- c("1TND_B","1AGR_A","1TAG_A","1GG2_A","1KJY_A","4G5Q_A")
files <- get.pdb(ids, split = TRUE)
# Extract and align the chains we are interested in
pdbs <- pdbaln(files, fit = TRUE)
# Print to screen a summary of the 'pdbs' object
pdbs
```

## Including Plots

You can also embed plots, for example:



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
